Synthesizing Slow Motion Periodic Videos via Circular Coordinate Reshuffling And Voting

### 2018-01-17 Paper/paper.tex
Finishing up pseudocode

\begin{algorithm}[t]
  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
  \begin{algorithmic}[1]
    \Procedure{ReorderVideo}{$X$, weighted, median} \\
    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames}
    \State $\hat{X} \gets$ 1D ISOMAP(X)
    \State $d \gets$ fundamental period estimate of $\hat{X}$
    \State $Y \gets SW_{d}[X[n]] \in \mathbb{R}^{WHd}$, with $M = N-d+1$ frames
    \State Perform SVD $Y = USV^T$, $\hat{Y} \gets V^TY$
    \State $I \gets dgm_1[\hat{Y}] = ((b_1, d_1), ... (b_k, d_k))$
    \State $i \gets \argmax_{i}[d_i - b_i]$, $\sigma \gets b_i + \frac{1}{2}(d_i - b_i)$
    \State $d_{ij} \gets ||\hat{Y}_i - \hat{Y}_j||_2$
    \If {weighted}
        \State $A_{ij} \gets e^{-d_{ij}^2/\sigma}$
    \Else
        \State $A_{ij} \gets \left\{ \begin{array}{cc} 1 & d_{ij} \leq \sigma \\ 0 & \text{otherwise} \end{array} \right\}$
    \EndIf
    \State $A_{ii} \gets 0, D_{ii} \gets \sum_{j=1}^M A_{ij}, D_{i, j \neq i} \gets 0$, $L \gets D - A$
    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zero-crossings
    \State $\theta \gets \cos^{-1}(v_2/v_1)$
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

where $\tau$ is a step size and $d$ is the dimension of the embedding.  In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.  In theory, a sliding window embedding of a single generic observation function of a dynamical system of intrinsic dimension $m$ can be reconstructed \cite{takens1981detecting}.
Talk about fundamental frequency estimation \cite{Mcleod05asmarter}

@@

>>>>

\begin{algorithm}[t]
    \caption{Laplacian Circular Coordinates}
    \begin{algorithmic}[1]
    \Procedure{CircCoords}{$X$, $L$}
    \State $\hat{X} \gets $ image pyramid level $L$ of $X$
    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{N \times N}$
    \State $y \gets$ 1D ISOMAP($Y$)
    \State $d \gets$ fundamental period estimate of $y$
    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times Nd}$, $M = N-d+1$

    \State $I \gets dgm_1[Z] = ((b_1, d_1), ... (b_k, d_k))$
    \State $i \gets \argmax_{i}[d_i - b_i]$, $\sigma \gets b_i + \frac{1}{2}(d_i - b_i)$
    \State $d_{ij} \gets ||Z_i - Z_j||_2$
    \If {weighted}
        \State $A_{ij} \gets e^{-d_{ij}^2/\sigma}$
    \Else
        \State $A_{ij} \gets \left\{ \begin{array}{cc} 1 & d_{ij} \leq \sigma \\ 0 & \text{otherwise} \end{array} \right\}$
    \EndIf
    \State $A_{ii} \gets 0, D_{ii} \gets \sum_{j=1}^M A_{ij}, D_{i, j \neq i} \gets 0$, $L \gets D - A$
    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zcs
    \State $\theta \gets \cos^{-1}(v_2/v_1)$\\
    \Return ($\theta$, d)
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
  \begin{algorithmic}[1]
    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
    \State Perform SVD $X = USV^T$, $\hat{X} \gets US$
    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times Nd}$, $M = N-d+1$
    \If {median}
        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
    \Else
        \State Order first frames in each window by $\theta$
    \EndIf
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

where $\tau$ is a step size and $d$ is the dimension of the embedding.  In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.  In theory, a sliding window of dimension $2m+1$ of a single generic observation function of a dynamical system of intrinsic dimension $m$ is a topological embedding of the original state space \cite{takens1981detecting}.

Talk about fundamental frequency estimation \cite{Mcleod05asmarter}

@@

Advantage of Eulerian is that everything is linear (can use SVD to compress)

Interpolated windows can be projected back to pixel space one by one to save memory (Line~\ref{algline:medianconsensus} of Algorithm~\ref{alg:videoreordering})
